Tensor anisotropy as a tracer of cosmic voids

### 2015-05-19 RefereeResponse.md

Conceptual:
==

1. **It seems that part of the motivation for using FA is that it is very well correlated with lambda_1, at low lambda_1. FA is a rather interesting quantity in itself, differentiating haloes and voids from filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The authors should more clearly articulate why this might be, if there is a reason. The FA being "conceived to quantify the anisotropy of the diffusivity of water molecules through cerebral tissue in nuclear magnetic resonance imaging" should be elaborated on; this does not clarify the usefulness of the FA for cosmologists. Conceptually, I also wonder: do filaments and walls behave differently from each other in FA, or do they both have FA ~ 1?**

      Response: 
      - Although lambda_1 is the defining property of voids when using the T-web/V-web (1st paragraph of subsec 3.2.), the FA exihibit a key advantage that makes it a better void tracer (please refer to 3rd paragraph of subsec. 3.2 of the new version).
      - Now it is explicitly explained why the FA, as defined in the context of MRI, is useful to cosmologist (6th paragraph of introduction and 1st paragraph of subsec 3.1).
      - A new figure (Fig 3.) was prepared. Histograms of the volume contribution of each environment for each value of the FA (3rd paragraph of subsec. 3.2).

### 2015-05-19 cosmic_voids.tex
Response of the first issue. New figure and explanations

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure*}
\centering

  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_delta.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_environment.pdf}

  \captionof{figure}{\small Overdensity (upper left) and Fractional
    Anisotropy (upper right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) 
    calculated over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin. This information is necessary to 
    define void boundaries in the watershed algorithm. The vertical lines 
    show the equivalent threshold values for the T-Web and V-web in order 
    to have voids composed by cells with Fractional Anisotrop equal or 
    less than $0.95$. This threshold on the eigenvalues does not influence 
    our computations. We show it as a guide to readers familiar with the
    order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

@@

In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The right panel shows the correlation between $\lambda_1$ and $\delta$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the FA. This shows that the
overdensity has a large scatter at fixed $\lambda_1$.

% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, }
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

%.........................................................................
%FIGURE 3: volume functions
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG1.pdf}

>>>>

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure}
\centering

  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.30\textheight]{delta_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.30\textheight]{FA_L1.pdf}  
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.30\textheight]{FA_delta.pdf}

  \captionof{figure}{\small Density contrast (top) and Fractional
    Anisotropy (middle) with respect to the eigenvalue $\lambda_1$ 
    and with respect to each other (bottom) for each web scheme (T-Web, 
    continous lines. V-Web, dashed lines) calculated over all grid cells 
    in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin. This information is necessary to 
    define void boundaries in the watershed algorithm. The vertical lines 
    show the equivalent threshold values for the T-Web and V-web in order 
    to have voids composed by cells with Fractional Anisotrop equal or 
    less than $0.95$. This threshold on the eigenvalues does not influence 
    our computations. We show it as a guide to readers familiar with the
    order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

\end{figure}
%.........................................................................

%-------------------------------------------------------------------------
%FIGURE 3: Histograms for each environment regarding the FA value
\begin{figure}
\centering

  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_environment.pdf}

  \captionof{figure}{\small Volume of each environment per FA 
  ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA ($dV/dFA$).
  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
  each line represents the volume contribution of the respective 
  environment to the total volume with the same FA value. Above FA=0.95,
  only sheets and filaments contribute to all the volume of the simulation
  within that range of FA.}
  \label{fig:FA_environment}

\end{figure}
%.........................................................................

@@

% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\before{In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The right panel shows the correlation between $\lambda_1$ and $\delta$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the FA. This shows that the
overdensity has a large scatter at fixed $\lambda_1$.}

\after{In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  The top panel shows the correlation between 
$\lambda_1$ and $\delta$ for all the grid cells in the simulation while the 
bottom panel shows the correlation between $\lambda_1$ and the FA. The middle 
panel shows the correlation between $\delta$ and the FA. This shows that the 
density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
small values of the density remain still associated to low values of the FA.}

\after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, the 
eigenvalue $\lambda_1$ presents, along with the density, an undesirable 
feature for a void tracer. As we move out from inner parts of voids to outer 
parts, $\lambda_1$ and the density increase monotonically, making unclear 
where to set the frontier of voids. On the other hand, the FA naturally 
indicates the real frontier as regions where anisotropic collapse begin to 
dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
mainly to sheets and, to a lesser extent, to filaments.}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

%.........................................................................
%FIGURE 4: volume functions
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG1.pdf}
